---

output: html_document
---
# Packages
The app relies on the following packages
```{r}

library(shiny)
library(shinythemes)
library(tidyverse)
library(stats4)
library(scales)
library(plotly)
library(shinycssloaders)
library(googledrive)
library(googlesheets4)
library(DT)
library(tidybayes)
library(ggtext)
library(cowplot)

```

# Code sources

Beta distribution parameters 
calculated from mean and variation is sourced from [this](https://stats.stackexchange.com/questions/12232/calculating-the-parameters-of-a-beta-distribution-using-the-mean-and-variance/12239#12239) Stack Excange post by [Dave Kincaid](https://stats.stackexchange.com/users/118/dave-kincaid)
```{r}
normalbeta <- function(mu, var) {
  alpha0 <- ((1 - mu) / var ^ 2 - 1 / mu) * mu ^ 2
  beta0 <- alpha0 * (1 / mu - 1)
  list(alpha0 = alpha0, beta0 = beta0)
}
```

Exact solution to the probability of any difference between the groups is sourced from [Introduction to Empirical Bayes](http://varianceexplained.org/r/empirical-bayes-book/) by [Dabid Robinson](https://twitter.com/drob)
```{r}
h <- function(alpha_a, beta_a,
              alpha_b, beta_b) {
  j <- seq.int(0, round(alpha_b) - 1)
  log_vals <-
    (
      lbeta(alpha_a + j, beta_a + beta_b) - log(beta_b + j) -
        lbeta(1 + j, beta_b) - lbeta(alpha_a, beta_a)
    )
  1 - sum(exp(log_vals))
}
```


# Further reading
For a demonstration on the principles underlying the app, see [this](https://discourse.datamethods.org/t/empirical-bayes-for-rct-interpretarion/2922) Datamethods post by Fernando Zampieri [@f_g_zampieri](twitter.com/f_g_zampieri)

For an introduction to the principles underlying this use of beta distributions see [this](https://karinknudson.com/dirichletprocesses.html) excellent post by [Karin Knudson](https://twitter.com/karinknudson) 

For a wider introduction to empirical bayes in R see [Introduction to Empirical Bayes](http://varianceexplained.org/r/empirical-bayes-book/) by [Dabid Robinson](https://twitter.com/drob)


# Author
Lars Mølgaard Saxhaug 
[@load_dependent](https://twitter.com/load_dependent)

Use and share freely!

